Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-07-08 Manuscript/manuscript.Rmd
resolved conflict
grammar edit

![**SMOTE re-sampling coupled with distance-type predictors yielded optimal MCCs across resolution for cell line specific models.** Performances of random forest classification models built on each of the 3 predictor types includeing (A-B) OC, (C-D) OP, and (E-F) Distance, and across both the GM12878 and K562 cell lines. Within each cell line, predictor type, and resolution, chromosome-specific training data was re-sampled using different techniques including no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and *Synthetic Minority Over Sampling TEchnique* (SMOTE; purple). Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v2.png)

>>>>

![**SMOTE re-sampling coupled with distance-type predictors yielded optimal MCCs across resolution for cell line specific models.** Performances of random forest classification models built on each of the 3 predictor types including (A-B) OC, (C-D) OP, and (E-F) Distance, and across both the GM12878 and K562 cell lines. Within each cell line, predictor type, and resolution, chromosome-specific training data was re-sampled using different techniques including no re-sampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and *Synthetic Minority Over Sampling TEchnique* (SMOTE; purple). Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v2.png)
